---
title: "econ_defend_analyses"
author: "LBE"
date: "2024-01-24"
output: html_document
---

# SETUP

``` {r}
library(tidyverse)
library(emmeans)
library(lme4)
library(ggalluvial)
library(vegan)
library(rstatix)
library(sf)
library(ggrepel)
library(ggspatial)
library(cowplot)
library(ggpubr)
library(pairwiseAdonis)

load("../data/iriomote_master.RData")

```
# STUDY SITE MAP
## Figure 1

```{r, message=FALSE}
sf::sf_use_s2(FALSE) #fixes an sf error

locations <- tibble(reef = c("Nata", "Sonai", "Unarizaki"), lat = c(24.4278,24.3814, 24.4273), long = c(123.7949, 123.7477, 123.7637))

geo.box <- c(xmin = 123.4, xmax = 123.95, ymin = 24.2, ymax = 24.5)

#too big for GitHub but freely available at https://www.ngdc.noaa.gov/mgg/shorelines/
L1_gshhg_f <- read_sf("../data/map/GSHHS_f_L1.shp") %>%
   st_crop(geo.box)

figure_1 <- ggplot(data = L1_gshhg_f) +
   geom_sf()+
   coord_sf()+
   geom_point( data = locations, 
               aes(x = long, y = lat), 
               fill = c("#87d1e0","#dfb0ce", "#c8d1a2"), 
               size = 4, 
               pch = 21) +
   geom_label_repel(data = locations, 
                    force_pull = 0.3, 
                    direction = 'y', 
                    label.size = NA, 
                    fill = NA, 
                    nudge_y = 0.02, 
                    nudge_x = -0.01, 
                    aes(x = long, y = lat, label = reef, segment.color = "black")) +
   annotate(geom = "text", 
            x = 123.83, 
            y = 24.33, 
            label = "Iriomote", 
            colour = "black") +
   annotation_scale() +
   annotation_north_arrow(style = north_arrow_fancy_orienteering, 
                          height = unit(1.5, "cm"), 
                          width = unit(1.5, "cm"), 
                          location = "tl") +
   scale_x_continuous("", expand = c(0.0008,0.0008)) +
   scale_y_continuous("") +
   theme_classic() +
   theme(panel.border = element_rect(colour = "black", fill=NA, size=0.5),
         axis.text = element_text(family = "Arial", size = 12))

figure_1


# japan inset map

world_map <- map_data("world", 'japan') #ggplot2

iriomote_inset <- ggplot(world_map, aes(x = long, y = lat, group = group)) +
   geom_polygon(fill="lightgray", colour = "black") +
   geom_segment(aes(y = 35, yend = 25.5, x = 123.8, xend = 123.8),
                arrow = arrow(length = unit(0.3,"cm")), linewidth = 0.2) +
   geom_rect(ymin = 24.2, ymax = 24.5, xmin = 123.6, xmax = 124, colour = "red", fill = NA, linewidth = 0.3)+
   annotate(geom = "text", x = 126, y = 45.5, label = "Japan" , size = 3) +
   theme_void()+
   theme(legend.position = 'none',
         panel.border = element_rect(colour = "black", fill=NA, linewidth = 0.5))
iriomote_inset

#' Ok now we have a decent overview map and high res Iriomote map, let's join them!

iriomote_join <- ggdraw() +
   draw_plot(Figure_1) +
   draw_plot(iriomote_inset, x = 0.7, y = 0.8, width = 0.2, height = 0.15 ) 
iriomote_join


# ggsave('Iriomote_sites.png', bg="transparent")

```
# AGGRESSION 
## sampling design
```{r sampling design, message = F, }
iriomote_master_aggro %>% 
   mutate(yr = as.factor(year(date)))%>%
   group_by(yr, reef) %>% 
   summarise(n=length(unique(observation))) %>% #stop here for detailed
   group_by(yr) %>% 
   summarise(n=sum(n))

```
##prepare data

this is analysing counts of passive vs aggressive encounters, on an individual level i.e. what's the average proportion of encounters that have an aggressive outcome per individual... in other words the focal follow is the unit of replication. 

```{r data prep}

#data for analysis
ind_agg <- iriomote_master_aggro %>% 
   mutate(yr = as.factor(year(date))) %>% 
   group_by(yr, outcome, observation) %>% 
   filter(outcome == 'a' | outcome == 'p') %>%
   count(outcome) %>% 
   pivot_wider(names_from = outcome, values_from = n, values_fill = 0) %>% 
   mutate(prop_aggro = a/(a+p)) 

#summarized data for plots
ind_agg_summ <- ind_agg %>% 
   group_by(yr) %>% 
   summarise(avg = mean(prop_aggro),
             SEM = sd(prop_aggro)/sqrt(length(prop_aggro)),
             n = length(prop_aggro),
             med = median(prop_aggro))

```
##Figure 2a

```{r plot data, message = F}
figure_2a <- ggplot() +
     geom_jitter(data = ind_agg, 
                  aes(x = yr, y = log10(prop_aggro)), 
                  stat = "identity", 
                  position = "jitter", 
                  alpha = 0.3, 
                  set.seed(42), 
                  shape = 21, 
                  fill = "#217a8d") +
   geom_boxplot(data = ind_agg, 
                aes(x = yr, y=log10(prop_aggro)),
                alpha = 0.7, 
                fill = "#217a8d", 
                width = 0.3) +
   #mean points   
   geom_point(data = ind_agg_summ, 
                  aes(x=yr, y=log10(avg))) +
   geom_errorbar(data = ind_agg_ovr, 
                 aes(x=yr, ymin = log10(avg - SEM), ymax = log10(avg + SEM)), 
                 width = 0, 
                 linewidth = 0.8) +
   geom_vline(xintercept = 1.5, 
              linetype = "dashed", 
              colour = "grey") +
   labs(x = "", 
        y = "Aggressive interaction log10(prob)") +
   theme_classic() +
   theme(axis.text.y = element_text(family = "arial", size=14),
         axis.text.x = element_blank(),
         axis.title = element_text(size = 14)) +
   scale_x_discrete(expand = c(0,0.5))

```

##Stats
Q. If an encounter occurs, has the probability of this encounter outcome changed (ie passive vs aggressive)  
 *YES, the proportions of passive vs aggressive interactions differ significantly over the years (X-square test, X-square= 24.8, df=3, p<0.0001). This difference is driven by the 2016/2017 drop in aggressive levels (pairwise_chisq_gof_test: X23.6, p=0.00000118)*

```{r}
# make contingency table

agg_contgcy <- iriomote_master_aggro %>%
   mutate(yr = as.factor(year(date))) %>%
   filter(outcome %in% c('a','p')) %>% 
   group_by(yr) %>%
   count(outcome) %>% 
   pivot_wider(names_from = yr, values_from = n) %>% 
   select(-outcome) #comment out to see what is what...

# run tests
chisq.test(agg_contgcy)
pairwise_chisq_gof_test(agg_contgcy) 

```

# CORAL SURVEYS

## sampling design
``` {r, message = FALSE}

iriomote_master_coral %>% 
    mutate(yr = (year(date)),
           tran = as.character(transect))%>%
    group_by(yr, site, depth) %>% 
    summarise(n=max(transect)) %>% #stop here for detailed breakdown
    group_by(yr) %>% 
    summarise(n=sum(n))

```

## prepare data
We want to separate Acropora cover, and pool by transect

``` {r, message = F}
coral_species <- iriomote_master_coral %>% 
   dplyr::mutate(acropora = str_detect(string = taxa, pattern = "Acropora"),
                 acropora = str_replace_all(acropora, "TRUE", "Acropora"),
                 acropora = str_replace_all(acropora, "FALSE", "Other")) %>% 
   dplyr::filter(coral==1) %>% 
   mutate(yr = (year(date)),
          tran_ID = str_c(yr,site,depth, transect, sep = "_")) %>%
   group_by(yr,site,depth,transect,acropora) %>%
   summarise(pc.coral = (sum(points))) 
```


## summary stats

Live coral cover summary stats
``` {r, message = FALSE}
# Live coral cover by taxa
coral_species_avg <- coral_species %>% 
   group_by(yr, acropora) %>% 
   summarise(mean_cr = mean(pc.coral),
             SEM_cr = sd(pc.coral)/sqrt(length(pc.coral)))

# Live coral cover overall
coral_species %>% 
   group_by(yr, site, depth, transect) %>% 
   mutate(ovr.coral = sum(pc.coral)) %>% 
   group_by(yr) %>% 
   summarise(mean_cr = mean(ovr.coral),
             SEM_cr = sd(ovr.coral)/sqrt(length(ovr.coral)))

```
## Stats

Q. Has coral cover declined/recovered since bleaching event?
 *YES, There is a significant interaction between year and coral taxa, suggesting that the different taxa changed differently over the surveyed years (Figure 2a, mixed effects model, (chisquare(3, 136) = 12.169, p = 0.007;). The interaction was driven by a 77% decline in mean Acropora cover between 2016 and 2017, and a further 7% decline in 2018 (2016 mean Acropora % cover ± SEM: 18.6 ± 3.92; 2017: 4.29 ± 0.9; 2018: 3 ± 0.59. Acropora coral cover has recovered in 2022*

```{r}
null.coral <- lmer(sqrt(pc.coral) ~ as.factor(yr) * acropora + (1|site), data = coral_species, REML = FALSE)
alt.coral <- lmer(sqrt(pc.coral)~ as.factor(yr) + acropora + (1|site), data = coral_species, REML = FALSE)
anova(null.coral, alt.coral)
summary(null.coral)

#assumptions
plot(fitted(null.coral), residuals(null.coral))
hist(residuals(null.coral))
qqnorm(residuals(null.coral))

#pairwise comps
coral_ls=(emmeans(null.coral, ~yr | acropora))
cld_corals <- multcomp::cld(coral_ls, Letters=letters, sort=F)
pairs(coral_ls)
plot(coral_ls)

```
## Figure 2b
``` {r 'figure_2b'}

#pull out IQR values for annotations
IQR <- layer_data(ggplot(data = coral_species, aes(x=factor(yr), y=pc.coral, fill = acropora))+
                     geom_boxplot()) %>% 
   pull(ymax)
   
#add to pairwise comp data
cld_corals <- cld_corals %>% 
   arrange(yr) %>% 
   mutate(IQRx = IQR+3)

#plot
figure_2b <- ggplot()+
   # raw data values
   geom_point(data = coral_species, 
              aes(x = factor(yr), y = pc.coral, fill = acropora), 
              shape = 21, alpha =0.3, position=position_jitterdodge()) +
   # boxplots
   geom_boxplot(data = coral_species, 
                aes(x=factor(yr), y=pc.coral, fill = acropora),
                size = 0.6, alpha = 0.7, colour = 'black', outlier.shape = NA) +
   # means
   geom_point(data = coral_species_avg, 
              aes(x=as.factor(yr), y= mean_cr, fill = acropora), 
              position=position_dodge(width=0.75), size = 2.5) +
   # mean SEMs
   geom_errorbar(data = coral_species_avg, 
                 aes(x=as.factor(yr), ymin = (mean_cr-SEM_cr), ymax = (mean_cr+SEM_cr), group = acropora), 
                 width=0, linewidth =.9, position=position_dodge(width=0.75)) +
   # multicomp annotations
   geom_text(data = cld_corals, 
             aes(label = .group, x= as.factor(yr), y = IQRx, group = acropora), 
             position=position_dodge(width=0.75)) +
   # make it look nice
   scale_fill_manual(values = c("orange","#78b792"))+
   scale_colour_manual(values = c("orange","#78b792"))+
   geom_vline(xintercept = 1.5, linetype = "dashed", colour = "grey")+
   labs(x = "Year", y = "Coral cover (%)") +
   
   #theme
   theme_classic()+
   theme(axis.text.y = element_text(family = "Arial", size = 14),
         axis.text.x = element_text(family = "Arial", size = 14),
         axis.title.y = element_text(size=14,margin = margin(t = 0, r = 0.35, b = 0, l = 0, unit = "cm")),
         axis.title.x =  element_text(family = "Arial", size = 14),
         legend.title = element_blank(),
         legend.position = "bottom")
figure_2b
```

#FISH SURVEYS

##sampling design

```{r, message =F}
iriomote_master_fish %>% 
   mutate(yr = as.factor(year(date)))%>%
   group_by(yr, location, depth) %>% 
   summarise(n=max(transect)) %>% #stop here for detailed breakdown
   group_by(yr) %>% 
   summarise(n=sum(n))
```

##prepare data for sankey figure

We want to make sure that only top 5 ranked species gets labeled in the figure

``` {r, message = F}
fish_abund <- iriomote_master_fish %>%
   mutate(yr = as.factor(year(date)))%>%
   group_by(yr, species) %>%
   summarise(avg.abund = mean(abundance),
             sem.abund = sd(abundance)/sqrt(length(abundance)))%>%
   mutate(
      rank = rank(desc(avg.abund)),
      lab = replace(species, rank >5,""))
fish_abund

# only write out labels each year for top 5 ranked species, that haven't been labeled in previous years

labs_16 <- fish_abund %>%
   filter(yr == 2016 & rank<5)

labs_17 <- fish_abund %>%
   filter(yr == 2017 & rank<5) %>% 
   mutate(lab = replace(lab, lab%in%labs_16$lab == T, ""))

labs_18 <- fish_abund %>%
   filter(yr == 2018 & rank<5) %>% 
   mutate(lab = replace(lab, lab%in%labs_16$lab, ""),
          lab = replace(lab, lab%in%labs_17$lab, ""))

labs_22 <- fish_abund %>%
   filter(yr == 2022 & rank<5) %>% 
   mutate(lab = replace(lab, lab%in%labs_16$lab, ""),
          lab = replace(lab, lab%in%labs_17$lab, ""),
          lab = replace(lab, lab%in%labs_18$lab, ""))

# merge with remaining data from fish ranked >5
fish_sankey <- fish_abund %>% 
   filter(rank>=5) %>% 
   bind_rows(labs_16, labs_17, labs_18, labs_22)

top5_sp <- fish_abund %>%
   group_by(yr) %>%
   slice_min(order_by = rank,n = 5) %>%
   ungroup() %>%
   distinct(species)
```

### prepare colour data

``` {r}
cols_12 <- tibble(value = c("#1c355e", # argentatus (order if unsorted)
                "#236093", # auriga
                "#217a8d", # citrinellus 3
                "#608eb5", # epphipium
                "#8393ca", # kleinii
                "#78b792", # lunulatus 1
                "#e4bd7d", # rafflesi 4
                "#f9ad81", # trifasc
                "#f5989d")) # unimac

#reorder colours by species rank
cols_reorder <- fish_abund %>%
   mutate(color = species%in%top5_sp$species) %>% 
          dplyr::group_by(species, yr) %>% 
   filter(color == TRUE,
          yr== 2016) %>% 
   arrange(rank) %>% 
   bind_cols(cols_12) %>% 
   rename(cols = "value") %>% 
   arrange(species) %>% 
   pull(cols)

cols_9 <-tibble(value = rep(c(cols_reorder), 5))

# make sure hat 2016 species highlights all top 5 species (not just that year)

col_44 <- fish_abund %>%
   mutate(color = species%in%top5_sp$species,
          cols = if_else(color == TRUE, 'red', 'grey')) %>%
   ungroup() %>% 
   select(cols)

row.n=0
for (i in 1:nrow(col_44)) {
   if(col_44[i,1]=="red"){
      row.n <- row.n+1
      col_44[i,1]= cols_9[row.n,]
      
   }}
col_44 <- pull(col_44[1])  
```

## Figure 3a

``` {r}
#setup the theme
theme_trans_sank <- theme_classic() +
   theme(legend.position = "none",
         panel.background = element_rect(fill = "transparent",colour = NA),
         plot.background = element_rect(fill = "transparent",colour = NA),
         axis.line = element_line(colour = 'white', size = 0.8),
         axis.text = element_text(colour = 'white', family = "Arial", size = 12),
         axis.ticks = element_line(colour = "white"),
         axis.title = element_text(colour = "white", size = 12, family = "Arial"))

# finally - let's plot!
figure_3a <- ggplot(data = fish_sankey, aes(x = yr, 
                                             stratum = species,
                                             alluvium = species,
                                             y = avg.abund,
                                             fill = species,
                                             label = lab)) +
   geom_vline(xintercept = 1.5, linetype = "dashed", colour = "grey") +
   geom_stratum(alpha = 0.9,  colour="white", decreasing = FALSE) +
   geom_alluvium(decreasing = FALSE) +
   geom_text (stat = "stratum", size =3, fontface = "italic",colour = "white", decreasing=FALSE) +
   labs(x = "", y = expression(Butterflyfish~density~(mean~"250m"^"-2")))+
   theme_classic() +
   theme(legend.position = "none")+
   # theme_trans_sank()+
   scale_y_continuous(expand = c(0,0))+
   scale_x_discrete(expand = c(0,0.2))+
   scale_fill_manual(values=col_44)

figure_3a
```
Cool! Let's also have a look at how these abundances differ between feeding guilds?

##Figure 3b
### Data wrangling
``` {r message = F}
# read classification file
 SppDistributionDiet <- read_csv("../data/SppDistributionDiet.csv") %>% 
    select(Chaetodon, diet_sk)
 
# first lets find any new species missing from the classification list in SppDistributionDiet
  no_feed_data <- iriomote_master_fish %>%
     mutate(yr = as.factor(year(date)),
           spp = str_replace(string = species, pattern = "C. ", ""))  %>% 
    left_join(x = ., y = SppDistributionDiet, by = c("spp"= "Chaetodon")) %>% 
    filter(is.na(diet_sk), 
           yr!=2022) %>% 
  pull(spp)
 
no_feed_sp <- unique(no_feed_data)

# Next let's classify them, based on Pratchett - "Biology of Butterflyfishes".
new_feed_data <- tibble(Chaetodon=no_feed_sp) %>% 
       bind_cols(diet_sk=c("invertivore", #burgessi
                     "facultative", #daedalma
                     "planktivore", #guentheri
                     "facultative", #mertensii
                     "invertivore", #modestus - actually Roa modestus, not a chaetodon
                     "facultative", #nipppn
                     "obligate", #pelewensis
                     "obligate", #plebius
                     "facultative", #quadrimaculatus
                     "obligate", # guesstimate based on parental feeding guilds (both obligates)
                     "facultative")) # weibeli
 Spp_diet_2020 <- bind_rows(SppDistributionDiet, new_feed_data)

 #' let's try again, shall we??
 fish_abun_feed <- iriomote_master_fish %>%
    mutate(yr = as.factor(year(date)),
           spp = str_replace(string = species, pattern = "C. ", ""))  %>% 
    left_join(x = ., y = Spp_diet_2020, by = c("spp"= "Chaetodon")) %>% 
    group_by(yr,diet_sk) %>%
    summarise(avg.abund = mean(abundance),
              sem.abund = sd(abundance)/sqrt(length(abundance))) %>% 
    mutate(lab = if_else(yr!="2017","", diet_sk))
 fish_abun_feed
 
 sum(is.na(fish_abun_feed$diet_sk))

```
###Fig

```{r}
 cols <- c("#217a8d", "#e4bf7b", "#79b793", "red") # facultative, invert,obligate


 figure_3b <- ggplot(data = fish_abun_feed, 
                            aes(x = yr, stratum = diet_sk, alluvium = diet_sk, y = avg.abund, fill = diet_sk, label = lab)) +
    geom_vline(xintercept = 1.5, linetype = "dashed", colour = "grey") +
    geom_stratum(alpha = 0.9,  colour="white", decreasing = FALSE) +
    geom_alluvium( decreasing = FALSE) +
    geom_text (stat = "stratum", size = 3,colour = "white", decreasing=FALSE, family ="Arial") +
    labs(x = "", y = expression(Butterflyfish~density~(mean~"250m"^"-2")))+
    theme_classic() +
    theme(legend.position = "none")+
    scale_y_continuous(expand = c(0,0))+
    scale_x_discrete(expand = c(0,0.2))+
    scale_fill_manual(values=cols)
 figure_3b 
```

## Stats

Q. Has the **overall** abundance of butterflyfish changed post-bleaching?
*NO, The main effect of yr is not statistically significant (Chisq(3,75) = 2.35, p = 0.5.  null_ttl_abundance: abund ~ yr + (1 | location)*

``` {r, message = F}
fish_abund_lme <- iriomote_master_fish %>%
   mutate(yr = as.factor(year(date)))%>%
   group_by(yr,location, depth, transect) %>%
   summarise(abund = sum(abundance))

fish_abund_lme
   
null_ttl_abundance <- lmer(abund~yr + (1|location), data = fish_abund_lme, REML = F)
alt_ttl_abundance <- lmer(abund~1 + (1|location), data = fish_abund_lme, REML = F)

anova(null_ttl_abundance, alt_ttl_abundance)
summary(null_ttl_abundance)


```

Q. Cool, does the feeding guild affect the abundances over time? 
*NO, there is no interaction between year and feeding guild (mixed effects model, chi-square 8.9 (9,3627), p = 0.4))*

```{r}
feed_abund <- iriomote_master_fish %>%
   mutate(yr = as.factor(year(date)),
          spp = str_replace(string = species, pattern = "C. ", ""))  %>% 
   left_join(x = ., y = Spp_diet_2020, by = c("spp"= "Chaetodon")) 

feed_null <- lmer(abundance ~ as.factor(yr)* diet_sk + (1|location), data = feed_abund, REML=F)
feed_alt <- lmer(abundance ~ diet_sk + as.factor(yr)  + (1|location), data = feed_abund, REML=F)
anova(feed_null, feed_alt)

summary(feed_null)

report(feed_null)

plot(fitted(feed_null), residuals(feed_null))
hist(residuals(feed_null))
qqnorm(residuals(feed_null))

```


Q. Has the **community** changed post-bleaching?
*YES - The species community of butterflyfishes was significantly  restructured in the four years post-bleaching (adonis F(3,73)=5.2, R2 = 0.18, p<0.001), and these differences were driven by the 2020 species composition which explained a total of 77% of variation between years  *

``` {r}
# find distinct species in dataset 
species_for <- iriomote_master_fish %>% 
   distinct(species) %>% 
   pull(species)

# start making a matrix, remove 0 rows
fish_wide <- iriomote_master_fish %>%
   mutate(yr = as.factor(year(date)))%>%
   tidyr::pivot_wider(names_from = species, values_from = abundance) %>% 
   dplyr::filter(rowSums(across(all_of(species_for)))>0) 

# pull treatment factors from matrix
years <- fish_wide %>% 
   select(location, depth, yr)

years_ <- fish_wide %>% 
   pull(6)

loc <- fish_wide %>% 
   pull(location)

#' remove factors from matrix
fish_matrix <- fish_wide %>% 
select(7:ncol(fish_wide),) 

#' try again
adon.results_all <- adonis2(fish_matrix ~ location + yr, method="bray",perm=999, data = years )
adon.results_all


adon.results_pair <- pairwise.adonis(x=fish_matrix, factors = years$yr)
adon.results_pair

#' assumptions
dis <- vegdist(fish_matrix) #Bray Curtis between samples
mod <- betadisper(dis, years_)
anova(mod)
plot(mod)
boxplot(mod)

```

Q. If you remove rare species, and just look at the dominant 5 species (= most ecologically relevant), has the abundance changed?
*No, there is no significant change in the abundance fo the 5 most common species over the four surveyed years (PERMANOVA, F1.8, p=0.06, r2 =0.06)*

```{r}
#first find the overall rare species in each year
fish_rarities <- iriomote_master_fish %>%
   dplyr::mutate(yr = as.factor(year(date)))%>%
   dplyr::group_by(yr,species) %>%
   summarise(avg.abund = mean(abundance),
             sem.abund = sd(abundance)/sqrt(length(abundance)))%>%
   mutate(
      rank = rank(desc(avg.abund)),
      lab = replace(species, rank >5,"")) %>% 
   dplyr::filter(rank<=4)

fish_commons <- fish_rarities %>% 
   pull(species) %>% 
   unique()

#then run the adonis again:

# start making a matrix, remove 0 rows
fish_wide <- iriomote_master_fish %>%
   mutate(yr = as.factor(year(date)))%>%
    dplyr::filter(species%in% fish_commons) %>%  #for reduced analysis only
   pivot_wider(names_from = species, values_from = abundance) %>% 
dplyr::filter(rowSums(across(all_of(fish_commons)))>0) # reduced dataset (with top sp only)

# pull treatment factor from matrix
years <- fish_wide %>% 
   select(location, depth, yr)

loc <- fish_wide %>% 
   pull(location)

#' remove factors from matrix
fish_matrix <- fish_wide %>% 
select(7:ncol(fish_wide),) #reduced

#run analysis
adon.results_all <- adonis2(fish_matrix ~ location + yr, method="bray",perm=999, data = years, )
adon.results_all

```

## Figure 3c

```{r}
#due to weirdness with extracting spider and polygon values from the plot() plots, you have to run this whole code at once, not line by line...

   # calculate the PCoA ordination sites' scores
 pcoa<- cmdscale(dis)
  plot(pcoa, asp=1)
    # calculate points
    PCoA <- as.data.frame(pcoa) %>% 
       mutate(years = years_)
     #calculate polygon shapes
   hull <- ordihull(pcoa, years_)
  
   unlist_hull <- tibble()
  for (i in names(hull)) {
      list_yr <- as_tibble(hull[[i]])
     list_yr[[3]] <- i
      unlist_hull <- bind_rows(unlist_hull, list_yr)
      }
  
   unlist_hull <- unlist_hull %>%  rename( years = "...3")
   
  
  # calculate spiders
   spider <- ordispider(pcoa, years_) 
   
   tb_spider <- tibble(centroid_x = spider[,1], centroid_y = spider[,2]) %>% 
      bind_cols(., PCoA) %>% 
      rename(start_x = V1,
             start_y = V2)
  
#run until here at once :)   
    
   # https://emilhvitfeldt.github.io/r-color-palettes/discrete.html 
v_cols = c("#236093","#217a8d", "#78b792", "#f5989d", "orange" )   

#### Pcoa_plot ----
# for transparent
theme_PCOA_bbg <- theme_classic() +
   theme(panel.background = element_rect(fill = "transparent",colour = NA),
         plot.background = element_rect(fill = "transparent",colour = NA),
         panel.border = element_rect(fill=NA, colour = "white", size = 1),
         axis.line = element_line(colour = 'white', size = 0),
         axis.text = element_text(colour = 'white', family = "Arial", size = 12),
         axis.ticks = element_line(colour = "white"),
         axis.title = element_text(colour = "white", size = 12, family = "Arial"),
         legend.position="top",
         legend.title = element_blank())


figure_3c <- ggplot()+
   geom_point(aes(x=V1, y=V2, shape = years, colour = years), data= PCoA) +
   geom_polygon(data = unlist_hull, 
                aes(x=Dim1, y=Dim2, colour = years, fill = years), alpha=0.1) +
   geom_segment(data = tb_spider,
                aes(x = start_x,
                    y = start_y,
                    xend = centroid_x,
                    yend  = centroid_y,
                    colour = years),
                alpha = 0.25) +
   theme_classic() +
   # theme_PCOA_bbg+
   scale_color_manual(values = v_cols) +
   scale_fill_manual(values = v_cols) +
   labs(x="pcoa 1", y= "pcoa 2") 
figure_3c

# ggsave('fish_community.png', bg="transparent")
```

#PUBLICATION FIGURES

```{r, message = F}
#Figure 1

figure_1
ggsave('../figures/Figure 1.png', bg="white")

#Figure 2

figure_2 <- ggarrange(figure_2a, figure_2b, ncol = 1, labels = "auto")
figure_2
# ggsave('../figures/Figure 2.png', bg = "white", width = 13, height = 20, unit = "cm", scale = 1.5)

#Figure 3

bottom_row <- plot_grid(figure_3b,figure_3c, labels = c("b", "c"))
figure_3 <- plot_grid(figure_3a, bottom_row, ncol = 1, labels ="a", rel_heights = c(1.5,1))
figure_3
 # ggsave('../figures/Figure 3.png', bg = "white", width = 21, unit="cm", scale = 1)
 
```
